---
title: "Developing Data Products <br><br> Project for Coursera Data Science Specialication <br><br> Auto Theft in Toronto"
author: "Parag Sengupta"
date: "April 24, 2018"
output: slidy_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# **Introduction - Auto Theft in Toronto**

This presentation is for a **project on Developing Data Products** as part of the Coursera Data Science Specialization.<br><br>
Analysis on: **Auto Theft in Toronto (2014-2017). **<br>
- 13,480 data records of which 13,435 pertains to the 2014-2017 period.<br><br>
Data Source: **Toronto Police Service, Public Safety Data Portal:** <br>
    http://data.torontopolice.on.ca/datasets/auto-theft-2014-to-2017 <br><br>
**Related links and file locations for this presentation** <br><br>
**App on shinyapps.io:** <br>
    https://paragsengupta.shinyapps.io/gtaautotheft/ <br><br>
**Source codes (Shiny ui.R and server.R) on GitHub repository:**<br>
    https://github.com/paragsengupta/DevelopingDataProductsProject <br><br>
**Presentation & Functionality on GitHub repository:**<br>
    https://github.com/paragsengupta/DevelopingDataProductsProject <br>
    (_R Markdown Slidy Presentation was used instead of R Presentation to create this pitch as RStudio v1.1.442 gave a message stating appshot of Shiny app objects - a key feature in this presentation - is not yet supported_)

# **Shiny App: Functionalities**

### **Main Panel:**

* Main Menu: 

    + Map
        
    + Chart
        
    + Data Table

- Main Display Zone: below the Main Menu<br><br>

### **SideBar Panel:**

- Slider to choose the year range for the Interactive Map

- Dropdown to choose whether to see All Neighbourhoods or Pick One

    + If Pick One chosen, Dropdown to choose the specific Neighbourhood by name

- Radio buttons for choose the Chart type to display in Main Display Zone

# **Shiny App in Real Action**
*Scroll down to see the complete application*
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(shiny)
library(shinythemes)
library(leaflet)
library(plotly)
library(DT)
server <- setwd("D:/Professional_n_Knowledge/Data Science John Hopkins/9 Developing Data Products/CourseProject/GTAAutoTheft")
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
shinyAppDir("D:/Professional_n_Knowledge/Data Science John Hopkins/9 Developing Data Products/CourseProject/GTAAutoTheft/", options = list(height=550))
```

# **Key Data Points (Variables) in the Auto Theft Data**

- Neighbourhoods: 

    + 140 different neighbourhoods included in the data<br>

        - **West Humber-Clairville has the highest auto theft occurrences**

- Premise Types: 

    + _3 key premise types, 1 to indicate outside and 1 for everything else_<br>

    + Apartment
    
    + Commercial
    
    + House
    
    + Outside
    
        - **Highest auto theft occurences reported from Outside**
    
    + Other
    
- Month and Day of Occurrence:

    + **Friday reported the highest auto theft in the week**
    
    + **October is the month reporting the highest auto thefts in the year**
    
